---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FDScraper

The goal of FDScraper is to scrape and analyze data from fd.nl ('Het Financieele Dagblad'). 

## Installation

You can install the development version of FDScraper from Github with:

``` r
# install.packages("devtools")
devtools::install_github("Glender/FDscraper")
```
## A simple example: scraping balance sheet data from fd.nl 

The package provides easy to use functions to scrape existing key figures from beurs.fd.nl:

```{r example_scrape}
library(FDScraper)

## scrape balance sheet data from Heineken
heineken_data <- extract_balance_data("https://beurs.fd.nl/noteringen/11770/heineken/kerncijfers")
print(heineken_data)

# Or from Ahold Delhaize
ahold_delhaize_data <- extract_balance_data("https://beurs.fd.nl/noteringen/11755/ahold-delhaize/kerncijfers")
print(ahold_delhaize_data)

```

Although this is nice to have, it doesn't provide us with a lot of numbers to play with. 
Therefore, the package also provides a function to find many urls from a broad range of companies:


```{r scrape_urls}

# we define two urls that contain a lot of references to companies
urls <- c(
  "https://beurs.fd.nl/analyse/amsterdam/aex/",
  "https://beurs.fd.nl/analyse/amsterdam/midkap/"
)

# scrape all sites
websites <- scrape_fd_urls(urls)

# show the first ten urls that we scraped
print(websites[1:10])
```
Next, we can scrape all the balance data for each company with `the scrape_fd_data` function:

```{r scrape_fd_data}

# scrape all the data of the 50 websites
data <- scrape_fd_data(websites)
```
Now we have collected all the data from those 50 companies, we can perform some simple analyzes.
For example, we first gonna remove missings, to deal with the warning message, and then we are going
to check whether Benford's Law applies on these numbers.

```{r scrape_fd_data2}

# only available via https://github.com/Glender/BenfordStats
library(BenfordStats)

# remove missings
results <- data[!is.na(data)]

# calculate observed and expected
first_digit_data <- BenfordStats::first_digit(results)

# We also calculate the expected probability of the first digit 
# for the first 9 numbers - those are our benchmark
expected <- round(BenfordStats::prob_first_digit(1:9), 2)
```

Finally, we are going to plot the results: 

```{r plot_data}
plot <- barplot(
  prop.table(table(first_digit_data)),
  ylim=c(0, .45),
  col= "#75AADB",
  main="Do Balance Sheet data conform to Benford's Law?",
  xlab = "First Digit",
  ylab = "Probability of First Digit"
)

lines(x = plot, y = expected, lty = 3)
points(x = plot, y = expected, pch = 19)

```
In conclusion, we can say that in general our observed data closely follows Benford's Law.
Of course, it is not a perfect fit, that can not be expected based on our limited sample size. 
